Studies of quantum dots

### 2017-02-26 Manuscript/paper.tex
Add more tables

\begin{table}
  \centering
  \caption{Ground state energy with $N$ particles and oscillator frequency $\omega$. The IM-SRG(2) results are given for $K=20$ shells (except for the $N=56$ results which are for $K=18$), employing a Hartree-Fock basis, the ordinary Coulomb interaction and the White generator.}
  \label{tab:SRGDMC-R20}
  \input{tab-ground}
\end{table}

\begin{table}
  \centering
  \caption{[[Addition energy]]}
  \input{tab-add}
\end{table}

\begin{table}
  \centering
  \caption{[[Removal energy]]}
  \input{tab-rm}
\end{table}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{fig-by-num-shells-6-2-ground-0-normal}
  \caption{[[...]]}
  \label{fig:by-num-shells-6-2-ground-0-normal}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{fig-by-freq-10-6-ground-0-normal}
  \caption{The behavior of ground state energy as a function of the oscillator frequency $\omega$.  The energy is normalized with respect to the Hartree-Fock values to make plot easier to see.  Lower frequency leads to stronger correlations and thereby a more difficult problem. [[the fact that CCSD and MP2 are really close may be just a coincidence, since they cross around 12 shells but then diverge again]]}
  \label{fig:by-freq-10-6-gs-0-normal}
\end{figure}

\begin{figure}
  \centering
  \begin{subfigure}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{fig-by-freq-10-6-add-0-normal}
    \caption{Addition energy}
    \label{fig:by-freq-10-6-add-0-normal}
  \end{subfigure}%
  \begin{subfigure}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{fig-by-freq-10-6-rm-1-normal}
    \caption{Removal energy}
    \label{fig:by-freq-10-6-rm-1-normal}
  \end{subfigure}
  \caption{The behavior of addition and removal energy as a function of the oscillator frequency $\omega$.  Like Figure \ref{fig:by-freq-10-6-gs-0-normal}, the energy is normalized with respect to the Hartree-Fock values.}
\end{figure}

@@

@@

The discrepeancy between IM-SRG results and the exact result is due to a combination of two factors: inadequate basis set, and operator truncation.
The former can be reduced by increasing the number of shells, and can be further alleviated by extrapolation techniques.

@@

[[TODO: add FCI, CCSD results to GS energy plots]]

@@

In Figure \ref{fig:gs} we display a selection of ground state energies calculated using the Hartree-Fock method, second-order (M\o ller-Plesset) perturbation theory (MPPT), and IM-SRG.  The exact result from diffusion Monte Carlo (DMC) is also shown as a dashed line \cite{PhysRevB.84.115302}.

@@

For our addition and removal energy calculations, the results are summarized in Figure \ref{fig:add} and Figure \ref{fig:rm} respectively.  The figures show the the addition/removal energies for Hartree-Fock, combined with IM-SRG and/or QDPT (Hartree-Fock is always included, as usual) [[better way to explain this? the figure labels are somewhat misleading too]].  The DMC results are also shown via dashed lines where they are known.

>>>>

\begin{table}
  \centering
  \caption{Ground state energy of quantum dots with $N$ particles and an oscillator frequency of $\omega$.  For every row, the calculations performed in a harmonic oscillator basis size with $K$ shells.}
  \label{tab:ground}
  \input{tab-ground}
\end{table}

\begin{table}
  \centering
  \caption{Addition energy of a selection of quantum dot systems.  See Table \ref{tab:ground} for details.}
  \label{tab:add}
  \input{tab-add}
\end{table}

\begin{table}
  \centering
  \caption{Removal energy of a selection of quantum dot systems.  See Table \ref{tab:add} for details.}
  \label{tab:rm}
  \input{tab-rm}
\end{table}

\begin{table}
  \centering
  % The siunitx package somehow makes the columns unnecessarily wide so we have to compensate by shrinking the text size :/
  \footnotesize
  \caption{Extrapolated ground state energies for quantum dots with fit uncertainties.  The uncertainties are computed from the approximate Hessian used in Levenberg-Marquardt fitting procedure.  Extrapolations are done using 5-point fits where the number of shells $K$ ranges between $K_{\text{stop}} - 4$ and $K_{\text{stop}}$ (inclusive).}
  \label{tab:ground-extrapolated}
  \input{tab-ground-extrapolated}
\end{table}

\begin{table}
  \centering
  \footnotesize
  \caption{Extrapolated addition energies for quantum dots with fit uncertainties.  See Table \ref{tab:ground-extrapolated} for details.}
  \label{tab:add-extrapolated}
  \input{tab-add-extrapolated}
\end{table}

\begin{table}
  \centering
  \footnotesize
  \caption{Extrapolated removal energies for quantum dots with fit uncertainties.  See Table \ref{tab:add-extrapolated} for details.}
  \label{tab:rm-extrapolated}
  \input{tab-rm-extrapolated}
\end{table}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{fig-by-num-shells-6-2-ground-0-normal}
  \caption{Ground state energy for quantum dots with 6 electrons plotted against $K$, the number of shells in the basis.  [[TODO: Results for FCI are from who?]] [[TODO: Add DMC results]]}
  \label{fig:by-num-shells-6-2-ground-0-normal}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{fig-by-freq-10-6-ground-0-normal}
  \caption{The behavior of ground state energy as a function of the oscillator frequency $\omega$, with 10 shells in the basis.  The energy is normalized with respect to the Hartree-Fock values to magnify the differences.  Lower frequency leads to stronger correlations and thereby a more difficult problem.  The fact that CCSD and MP2 are similar is likely coincidence as they cross at around 12 shells and then diverge again (not shown in this plot). [[TODO: Add DMC results if available]]}
  \label{fig:by-freq-10-6-gs-0-normal}
\end{figure}

\begin{figure}
  \centering
  \begin{subfigure}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{fig-by-freq-10-6-add-0-normal}
    \caption{Addition energy}
    \label{fig:by-freq-10-6-add-0-normal}
  \end{subfigure}%
  \begin{subfigure}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{fig-by-freq-10-6-rm-1-normal}
    \caption{Removal energy}
    \label{fig:by-freq-10-6-rm-1-normal}
  \end{subfigure}
  \caption{The behavior of addition and removal energy as a function of the oscillator frequency $\omega$, with 10 shells in the basis.  Like Figure \ref{fig:by-freq-10-6-gs-0-normal}, the energy is normalized with respect to the Hartree-Fock values.}
\end{figure}

@@

All calculations in this paper are performed with a relative numerical precision of about $10^{-5}$ or lower (sometimes \emph{much} lower).  This does not necessarily mean the results are as precise as $10^{-5}$, since numerical errors tend to accumulate at every step of the calculation, thus the precision of the final results may be an order of magnitude larger.

@@

The discrepancy between IM-SRG results and the exact result is due to a combination of two factors: inadequate basis set, and operator truncation.
The former can be reduced by increasing the number of shells, and can be further alleviated by extrapolation techniques.

@@

@@

In Figure \ref{fig:gs} we display a selection of ground state energies calculated using the Hartree-Fock method, second-order (M\o ller-Plesset) perturbation theory (MPPT), and IM-SRG.  Results from diffusion Monte Carlo (DMC) \cite{hoegberget2013thesis} are shown as a dashed line for comparison.

@@

For our addition and removal energy calculations, the results are summarized in Figure \ref{fig:add} and Figure \ref{fig:rm} respectively.  The figures show the the addition/removal energies for Hartree-Fock, combined with IM-SRG and/or QDPT (Hartree-Fock is always included, as usual) [[better way to explain this? the figure labels are somewhat misleading too]].  Results from diffusion Monte Carlo (DMC) \cite{PhysRevB.84.115302} are shown as a dashed line, where available.
